FTLR proof cases

### 2018-06-25 fully-abstract-comp/ftlr-proof-cases.tex
The FTLR does not actually need to apply to linear executable capabilities, since components aren't allowed to ever construct such capabilities.

\begin{lemma}
  \label{lem:ftlr-internal-lemma}
  If
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}
  \item $\Phi_S(\pcreg) = \Phi_T(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\_)$
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$
  \item $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$
  \item $\memSat{\Phi_S.\mem,\Phi_S.\stk,\Phi_S.\ms_\stk,\Phi_T.\mem}{W_M}$
  \item $W_\pcreg \oplus W_R \oplus W_M$ is defined.
  \item Theorem~\ref{thm:ftlr} holds for all $n' < n$.
  \end{itemize}
  Then
  \[
    \npair{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  In the following we will use the following: $\reg_S = \Phi_S.\reg$, $\reg_T = \Phi_T.\reg$, $\ms_S = \Phi_S.\mem$, $\ms_\stk = \Phi_S.\ms_\stk$, and $\stk = \Phi_S.\stk$.

@@

  In order to prove this, we first, we prove that one of the following holds:
  \begin{enumproof}
  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$.
  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$
  \item \label{case:ftlr:get-and-arith-op} All of the following hold: (includes simple cases: gettype, geta, getb,
    gete, getp, getl, lt, plus, minus, one case of move that can be handled
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
    \item $z \in \ints$
    \end{itemize}
  \item \label{case:ftlr:call} All of the following hold:
    \begin{itemize}
    \item $\callCond{\Phi_S,r_1,r_2,\offpc,\offsigma,\aaddr}$
    \item $r_1 \neq \rtmp{1}$ and $r_2 \neq \rtmp{1}$
    \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
    \item $\exec{\Phi_S(\pcreg)}$
    \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
      % domi: this condition doesn't make syntactic sense and is also not used.
    % \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $z \in \ints$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\rstk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item \[
        \begin{split}
          \Phi_S''.\reg = \Phi_S.reg      &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr+\calllen)}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
        \end{split}
      \]
    \item $\Phi_S''.\mem = \Phi_S.\mem$
    \item $\ms_{\stk\_\priv,S} = \Phi_S.\ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42}$
    \item $\Phi_S''.\stk = ((\aaddr+\calllen),\ms_{\stk\_\priv,S}) :: \Phi_S.\stk$
    \item $\Phi_S''.\ms_\stk = \Phi_S.\ms_\stk -
      \Phi_S.\ms_\stk|_{[\aaddr_\stk,\eaddr_\stk]}$
    \item $\baddr \leq \aaddr+\offpc \leq \eaddr$
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

@@

  In case \ref{case:ftlr:failed}, both executions go to $\failed$.
  In this case, the result follows vacuously by definition of $\lrol$ and $\lror$.
  \\\\
  In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
  steps, so both directions of $\lro$ are trivially satisfied.
  \\\\
  In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to conclude
  \[
    \npair[n-1]{(\Phi_S',\Phi_T')} \in \lro
  \]
  from the following facts:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}
    This follows from the corresponding assumption of this lemma and the fact that $\Phi_S \nstep[1]{\gc} \Phi_S'$ and Lemma~\ref{lem:ec-reasonable-antired}, \ref{lem:ec-reasonable-downwards-closed}, and \ref{lem:downwards-closed}.
  \item $\Phi_S'(\pcreg) = \Phi_T'(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\_)$:
    Follows from the definition of $\updPcAddr{}$ and the assumptions of this case.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item $\npair[n-1]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}, the definition of $\lrr$ and the fact that integers are always in $\lrvg{\trust}$ by definition.
  \item $\memSat[n-1]{\Phi_S.\mem,\Phi_S.\ms_\stk,\Phi_S.\stk,\Phi_T.\mem}{W_M}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item Theorem~\ref{thm:ftlr} holds for all $n'' < n-1$:
    follows from the corresponding assumption of this lemma, since $n - 1 < n$.
  \end{itemize}

  \lau{TODO: look through this case and find the place where the ''no seal cross boundary thing'' should have been used.
    (I have done this, and it does not seem necessary (?))}
  In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump. If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.} and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.} as this will cause the execution to fail.
  We need to let the target execution catch up.
  That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
  \[
    \Phi_T'' = \Phi_T
    \begin{array}[t]{l}
      \update{\mem.\aaddr_\stk}{42} \\
      \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
      \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
      \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\retoffset)}} \\
      \updReg{\rtmp{1}}{0}\\
      \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
      \updReg{\pcreg}{c_1'}\\
      \updReg{\rdata}{c_2'}
    \end{array}
  \]
  where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
  Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
  \[
    \npair[n-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  By assumption, we have $\npair[n]{(\reg_S(r_i),\reg_T(r_i))} \in \lrvg{\trust}(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
  We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
  Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrvg{\trust}$ we get
  $\npair[n-1]{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
  and w.l.o.g.\

@@

  First show: if $\lin = \normal$, then
  \[
    \npair[n-1]{(((\rx,\normal),\baddr,\eaddr,\aaddr),((\rx,\normal),\baddr,\eaddr,\aaddr))} \in \lrvg{\trust}(\purePart{W_R})
  \]
  First observe that by Lemma~\ref{lem:purePart-oplus} $\purePart{W_R} = \purePart{W_\pcreg}$.
  Further, by assumption, Lemma~\ref{lem:downwards-closed}, Lemma~\ref{lem:purePart-oplus}, and Lemma~\ref{lem:non-linear-pure}, we have
  \[
    \npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{}(\purePart{W_R})
  \]

@@

    To this end let $W' \future \purePart{W_R}$ and $n' < n-1$ and $\aaddr' \in [\baddr',\eaddr']$ be given, and show
    \[
      \npair[n']{(((\rx,\normal),\baddr',\eaddr',\aaddr'),((\rx,\normal),\baddr',\eaddr',\aaddr'))} \in \lre(W')
    \]
    If $[\baddr',\eaddr'] = \emptyset$, then this is trivial, so assume $[\baddr',\eaddr'] \neq \emptyset$.
    Further, for $n'' \leq n'$ assume
    \begin{itemize}
    \item $\npair[n'']{\reg_S',\reg_T'} \in \lrr(W_R')$
    \item $\memSat{\ms_S',\stk',\ms_\stk',\ms_T'}{W_M'}$
    \item $W' \oplus W_R' \oplus W_M'$ is defined
    \end{itemize}
    and show
    \[
      \npair[n'']{\left(
          \begin{array}{l}
          (\ms_S',\reg_S'\update{\pcreg}{((\rx,\normal),\baddr',\eaddr',\aaddr')},\stk',\ms_\stk') \\
          (\ms_T',\reg_T'\update{\pcreg}{((\rx,\normal),\baddr',\eaddr',\aaddr')})
          \end{array}
         \right)} \in \lro
    \]
    To this end, we want to use the IH which means that we need the following:
    \begin{itemize}
    \item $\trust = \untrusted$ and $\npair[n'']{[\baddr',\eaddr']} \in \readCond{W'}$

@@

  By Lemma~\ref{lem:lro-anti-red-gen} it suffices to show
  \[
    \npair[n-1]{\Phi_S',\Phi_T'} \in \lro
  \]
  which follows from the induction hypothesis in the case where $\Phi_S'.\reg(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\_)$.
  In this case, the IH is applicable because we have the following:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S'$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}

    We know one of the following holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}
    If the latter is the case, then the result follows by Lemma~\ref{lem:downwards-closed}.

@@

  It remains to show the case where $\Phi_S'.\reg(\pcreg) \neq ((\rx,\lin),\baddr,\eaddr,\_)$

@@

\begin{proof}[Proof of Theorem~\ref{thm:ftlr}]
  By complete induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
  Assume
  \begin{itemize}
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{enumerate}[label={\roman*)}]
  \item \begin{itemize}
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item ${((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps.
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \end{itemize}
  \end{enumerate}
and show
\[
\npair{(c,c)} \in \lre(W)
\]
For $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

>>>>

\begin{lemma}
  \label{lem:ftlr-internal-lemma}
  If
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
  \item $\Phi_S(\pcreg) = \Phi_T(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$
  \item $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$
  \item $\memSat{\Phi_S.\mem,\Phi_S.\stk,\Phi_S.\ms_\stk,\Phi_T.\mem}{W_M}$
  \item $W_\pcreg \oplus W_R \oplus W_M$ is defined.
  \item Theorem~\ref{thm:ftlr} holds for all $n' < n$.
  \end{itemize}
  Then
  \[
    \npair{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  In the following we will use the following: $\reg_S = \Phi_S.\reg$, $\reg_T = \Phi_T.\reg$, $\ms_S = \Phi_S.\mem$, $\ms_\stk = \Phi_S.\ms_\stk$, and $\stk = \Phi_S.\stk$.

@@

  In order to prove this, we first, we prove that one of the following holds:
  \begin{enumproof}
  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$.
  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$
  \item \label{case:ftlr:get-and-arith-op} All of the following hold: (includes simple cases: gettype, geta, getb,
    gete, getp, getl, lt, plus, minus, one case of move that can be handled
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
    \item $z \in \ints$
    \end{itemize}
  \item \label{case:ftlr:call} All of the following hold:
    \begin{itemize}
    \item $\callCond{\Phi_S,r_1,r_2,\offpc,\offsigma,\aaddr}$
    \item $r_1 \neq \rtmp{1}$ and $r_2 \neq \rtmp{1}$
    \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
    \item $\exec{\Phi_S(\pcreg)}$
    \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
      % domi: this condition doesn't make syntactic sense and is also not used.
    % \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $z \in \ints$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\rstk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\normal),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item \[
        \begin{split}
          \Phi_S''.\reg = \Phi_S.reg      &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr+\calllen)}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
        \end{split}
      \]
    \item $\Phi_S''.\mem = \Phi_S.\mem$
    \item $\ms_{\stk\_\priv,S} = \Phi_S.\ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42}$
    \item $\Phi_S''.\stk = ((\aaddr+\calllen),\ms_{\stk\_\priv,S}) :: \Phi_S.\stk$
    \item $\Phi_S''.\ms_\stk = \Phi_S.\ms_\stk -
      \Phi_S.\ms_\stk|_{[\aaddr_\stk,\eaddr_\stk]}$
    \item $\baddr \leq \aaddr+\offpc \leq \eaddr$
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

@@

  In case \ref{case:ftlr:failed}, both executions go to $\failed$.
  In this case, the result follows vacuously by definition of $\lrol$ and $\lror$.
  \\\\
  In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
  steps, so both directions of $\lro$ are trivially satisfied.
  \\\\
  In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to conclude
  \[
    \npair[n-1]{(\Phi_S',\Phi_T')} \in \lro
  \]
  from the following facts:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
    This follows from the corresponding assumption of this lemma and the fact that $\Phi_S \nstep[1]{\gc} \Phi_S'$ and Lemma~\ref{lem:ec-reasonable-antired}, \ref{lem:ec-reasonable-downwards-closed}, and \ref{lem:downwards-closed}.
  \item $\Phi_S'(\pcreg) = \Phi_T'(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$:
    Follows from the definition of $\updPcAddr{}$ and the assumptions of this case.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item $\npair[n-1]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}, the definition of $\lrr$ and the fact that integers are always in $\lrvg{\trust}$ by definition.
  \item $\memSat[n-1]{\Phi_S.\mem,\Phi_S.\ms_\stk,\Phi_S.\stk,\Phi_T.\mem}{W_M}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item Theorem~\ref{thm:ftlr} holds for all $n'' < n-1$:
    follows from the corresponding assumption of this lemma, since $n - 1 < n$.
  \end{itemize}

  \lau{TODO: look through this case and find the place where the ''no seal cross boundary thing'' should have been used.
    (I have done this, and it does not seem necessary (?))}
  In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump. If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.} and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.} as this will cause the execution to fail.
  We need to let the target execution catch up.
  That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
  \[
    \Phi_T'' = \Phi_T
    \begin{array}[t]{l}
      \update{\mem.\aaddr_\stk}{42} \\
      \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
      \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
      \updReg{\rretc}{\sealed{\sigma',((\perm,\normal),\baddr,\eaddr,\aaddr+\retoffset)}} \\
      \updReg{\rtmp{1}}{0}\\
      \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
      \updReg{\pcreg}{c_1'}\\
      \updReg{\rdata}{c_2'}
    \end{array}
  \]
  where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
  Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
  \[
    \npair[n-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  By assumption, we have $\npair[n]{(\reg_S(r_i),\reg_T(r_i))} \in \lrvg{\trust}(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
  We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
  Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrvg{\trust}$ we get
  $\npair[n-1]{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
  and w.l.o.g.\

@@

  First show that
  \[
    \npair[n-1]{(((\rx,\normal),\baddr,\eaddr,\aaddr),((\rx,\normal),\baddr,\eaddr,\aaddr))} \in \lrvg{\trust}(\purePart{W_R})
  \]
  First observe that by Lemma~\ref{lem:purePart-oplus} $\purePart{W_R} = \purePart{W_\pcreg}$.
  Further, by assumption, Lemma~\ref{lem:downwards-closed}, Lemma~\ref{lem:purePart-oplus}, and Lemma~\ref{lem:non-linear-pure}, we have
  \[
    \npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{}(\purePart{W_R})
  \]

@@

    To this end let $W' \future \purePart{W_R}$ and $n' < n-1$ and $\aaddr' \in [\baddr',\eaddr']$ be given, and show
    \[
      \npair[n']{(((\rx,\normal),\baddr',\eaddr',\aaddr'),((\rx,\normal),\baddr',\eaddr',\aaddr'))} \in \lre(W')
    \]

    If $[\baddr',\eaddr'] = \emptyset$, then this is trivial, so assume $[\baddr',\eaddr'] \neq \emptyset$.
    Further, for $n'' \leq n'$ assume
    \begin{itemize}
    \item $\npair[n'']{\reg_S',\reg_T'} \in \lrr(W_R')$
    \item $\memSat{\ms_S',\stk',\ms_\stk',\ms_T'}{W_M'}$
    \item $W' \oplus W_R' \oplus W_M'$ is defined
    \end{itemize}
    and show
    \[
      \npair[n'']{\left(
          \begin{array}{l}
          (\ms_S',\reg_S'\update{\pcreg}{((\rx,\normal),\baddr',\eaddr',\aaddr')},\stk',\ms_\stk') \\
          (\ms_T',\reg_T'\update{\pcreg}{((\rx,\normal),\baddr',\eaddr',\aaddr')})
          \end{array}
         \right)} \in \lro
    \]
    To this end, we want to use the IH which means that we need the following:
    \begin{itemize}
    \item $\trust = \untrusted$ and $\npair[n'']{[\baddr',\eaddr']} \in \readCond{W'}$

@@

  By Lemma~\ref{lem:lro-anti-red-gen} it suffices to show
  \[
    \npair[n-1]{\Phi_S',\Phi_T'} \in \lro
  \]
  which follows from the induction hypothesis in the case where $\Phi_S'.\reg(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$.
  In this case, the IH is applicable because we have the following:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S'$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}

    We know one of the following holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
    If the latter is the case, then the result follows by Lemma~\ref{lem:downwards-closed}.

@@

  It remains to show the case where $\Phi_S'.\reg(\pcreg) \neq ((\rx,\normal),\baddr,\eaddr,\_)$

@@

\begin{proof}[Proof of Theorem~\ref{thm:ftlr}]
  By complete induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
  Assume
  \begin{itemize}
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{enumerate}[label={\roman*)}]
  \item \begin{itemize}
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item ${((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps.
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \end{itemize}
  \end{enumerate}
and show
\[
\npair{(c,c)} \in \lre(W)
\]
For $c=((\rx,\normal),\baddr,\eaddr,\aaddr)$.\\
